---
title: "First Knit"
author: "Moises Sales"
date: "August 19th, 2019"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  

###my answer     
  
Currently I am sitting in the back row at computer number 41. Normally I am seated towards the middle isle in some location so that I can have full view of the class so the seating area doesn't matter to me to much. I feel like moving seats around is a 3 to me since I mostly assume students who have difficutly seeing tend to sit closer to the front of the class. I have worked on class group assignments and I don't mind them.
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

###my answer     

I tend to go by my first name which is Moises. Closer people usually shorten that and call me Moi.
   
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

###my answer     
  
Currently I am trying to become a chemist and focus either on analytics or go to pharmaceutical school. For now I intend on focusing my schooling towards that and stats is part of my transfer credits.   
 




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

###my answer     
  
I have been to El salvador and slight parts of Mexico. I would enjoy visiting those in the future. I am not in the military but if I were drafted at some point I would most likely choose the Navy.   
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 

###my answer     
  
I plan on getting an A or a B in this class to maintain a good GPA. I'm not fully sure how all the assignments and class scheduling will work out since I added the class of today and still need to check out the syllabus fully.   
 





##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

###my answer   
  
I would roughly say I am at an 8 on in terms of knowing a computer. I have a computer at home and it runs off windows. I have internet access. I drive to class. I attended highschool at Lancaster High School and graduated in 2014. Currently I am looking for a new job.   
  




